---
title: "Norton Assignment 4"
author: "Jenny Norton"
date: "9/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

Return to the iris data set included in R. Examine the distributions of Sepal.Length and Sepal.Width. Produce a graph (or two) which represent these distributions. What can you say about the variation of Sepal.Length and Sepal.Width?

```{r}
library(tidyverse)
```

```{r}
str(iris)
```

```{r}
hist(iris$Sepal.Length, 
     labels = TRUE, 
     ylim = c(0,35))
```

```{r}
hist(iris$Sepal.Width,
     labels = TRUE, 
     ylim = c(0,40)) 
```

Sepal Length is mostly between 4.5 and 6.5 in size whereas the Sepal Width is mostly 2.75 to 3.25.


## Question 2

Examine how the categorical variable Species affects the distribution of Sepal.Length and Sepal.Width. Produce a graph (or two) which shows clearly the relationship you would like to demonstrate. Can the covariation here help explain some of the patterns we saw in first exploration?

```{r}
iris %>%
  group_by(Species) %>%
  ggplot() +
    geom_bar(aes(x = Sepal.Length, fill = Species), position = "dodge") +
    labs(title = "Sepal Length by Species")
```

```{r}
ggplot(data = iris) +
  geom_boxplot(aes(x = Sepal.Length, y = Species)) +
                 labs(title = "Sepal Length across Species",
       x = "Sepal Length",
       y = "Species")
```

```{r}
ggplot(data = iris) +
  geom_boxplot(aes(x = Sepal.Width, y = Species)) +
                 labs(title = "Sepal Width across Species",
       x = "Sepal Width",
       y = "Species")
```

```{r}
ggplot(data = iris,
       aes(x = Sepal.Length,
           y = Sepal.Width,
           color = Species
           )
          ) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, formula = y~x)
```

The longer Sepal Length gets, the wider Sepal Width is.  The species Setosa seems to get wider faster in comparison to the other two species.

## Question 3
Examine the distribution of Sepal.Width now for data in only the species virginica in the data set. What can you say about the distribution?

```{r}
iris %>%
  filter(Species == "virginica") %>%
  ggplot() +
  geom_histogram(aes(x = Sepal.Width, fill = Species), 
        binwidth = .25) +
  labs(title = "Sepal Width of Virginica Species",
       x = "Sepal Width")
```

Virginica's Sepal Width is mostly 2.75 to 3.0.

